%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Thomas}{DERUDDER}
\position{Site Reliability Engineer{\enskip\cdotp\enskip}Software Developer }
\address{40 avenue Clément Ader Montesson, France, (Paris)}
\mobile{(+33) 6-03-11-44-59}
\email{thomas@mypatch.fr}
%\dateofbirth{January 1st, 1970}
\homepage{www.mypatch.fr}
% \github{posquit0}
\linkedin{thomas-derudder-63080522b}
\gitlab{ripitchip}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}



%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Director of Research and Innovation}
  {Cégep de Sept-Îles\\175 Rue de la Vérendrye, \\Sept-Îles, QC G4R 5B7, Canada}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Internship Application for Software Engineer in embed development}
% How the letter is opened
\letteropening{Dear Dr. Laurent FERRIER,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\hspace{8cm}\makeclheader[L]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% \makecvfooter
%   {\today}
%   {Thomas Derudder~~~·~~~Cover Letter}
%   {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing to express my interest in a research internship under your supervision, as recommended by my professor, Mr. Peretti, who spoke highly of your innovative work in the field of telecommunications and railway tracking. I am a 4th-year computer science engineering student seeking a research internship opportunity to gain hands-on experience and apply theoretical knowledge in a real-world setting. I am available to start from mid-April and am looking for a position that will last until the end of August. With a strong foundation in computer science engineering and a passion for research, I am excited about the opportunity to contribute to your research team and learn from your expertise in aerial telecommunications systems and RFID technologies.

As a computer science engineering student, I have developed a solid background in programming, software development, and project management. My apprenticeship at the French Army Ministry has provided me with hands-on experience in creating automated clusters, managing projects, and sharing knowledge. Additionally, my experience as a FabLab creator and instructor in computer science and electronics has given me a deep understanding of embedded technologies and connected object construction. I am particularly drawn to your research group's diverse range of projects and expertise, and I am eager to learn and contribute to multiple areas, including linux systems, Internet of Things (IoT), wireless sensor networks, and RFID technologies. I believe that my skills in software development and project management could be valuable to your research endeavors, and I am excited about the opportunity to explore these areas in more depth.

I appreciate your dedication to advancing the field of telecommunications and railway tracking through innovative research. As someone who enjoys tackling new challenges and bringing a fresh perspective to projects, I believe I would be a suitable candidate for a research environment that encourages curiosity and exploration. I am interested in the opportunity to work on projects that have the potential to make a meaningful contribution to the field and advance our understanding of the subject matter.

Thank you for considering my application. I would be honored to discuss my qualifications further and explain in greater detail why I am a strong fit for this research internship. Please feel free to contact me to schedule a meeting or conversation. I look forward to the opportunity to learn from you and contribute to your research team.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
